---
title: "example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# oTools
Here is a brief overview of the package.

# Installation
This is how you install this package. 
```{r}

```

# Setup and load some example data
```{r setup, warning=FALSE}
suppressMessages(devtools::load_all())
suppressPackageStartupMessages(library(tidyverse))


# Load some data
birdData <- system.file("extdata", "birdData.csv", package = "oTools") |>
  read.csv()
greebData <- system.file("extdata", "greebData.csv", package = "oTools") |>
  read.csv()
ziggData <- system.file("extdata", "ziggData.csv", package = "oTools") |>
  read.csv()

birdSummary <- birdData |>
  group_by(sbjID) |>
  summarise(
    Bird = mean(corr)
  ) |>
  rename(SbjID = sbjID)
greebSummary <- greebData |>
  group_by(SbjID) |>
  summarise(
    Greeb = mean(corr)
  )
ziggSummary <- ziggData |>
  group_by(SbjID) |>
  summarise(
    Zigg = mean(corr)
  )

allSummary <- birdSummary |>
  left_join(greebSummary, by = "SbjID") |>
  left_join(ziggSummary, by = "SbjID")
```

# long2Matrix
This function converts the long format to the wide matrix format.
```{r, warning=FALSE, message=FALSE}
birdMatrix <- long2Matrix(
  birdData,
  idCol = "sbjID",
  corrCol = "corr",
  trialNCol = "trialN",
  summaryStats = TRUE
)

greebMatrix <- long2Matrix(
  greebData,
  idCol = "SbjID",
  corrCol = "corr",
  trialNCol = "trialN",
  summaryStats = TRUE
)

ziggMatrix <- long2Matrix(
  ziggData,
  idCol = "SbjID",
  corrCol = "corr",
  trialNCol = "trialN",
  summaryStats = TRUE
)
```

# matrix2Rel
This function calculates reliability given the matrix wide format produced by
`long2Matrix`. Note that if you don't have the `summaryStats` argument set to 
`TRUE`, this function will not work, but the equivalent results can be produced
using `splitHalf(wideMatrix, check.keys = FALSE)`.

```{r, warning=FALSE}
birdRel <- matrix2Rel(birdMatrix)
greebRel <- matrix2Rel(greebMatrix)
ziggRel <- matrix2Rel(ziggMatrix)

allRel <- c(birdRel$lambda2, greebRel$lambda2, ziggRel$lambda2)

ziggRel
```

# aggRel
This function calculates the aggregate reliability given a set of measures. 
Notice that more than 2 measures can be used here.

```{r, warning=FALSE}
tmp <- allSummary |> select(-SbjID)
aggRel(tmp, allRel)
```

# corMatrixPlot
This function creates a pairs plot of the correlation matrix. Notice the format
for lambda symbols.

```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=8}
lambda2 <- "\U03BB\U2082"

corMatrixPlot(
  data = allSummary |> select(-SbjID),
  reliability = allRel,
  nullInterval = c(-1, 0),
  rscale = 1 / 3,
  relSymbol = c(lambda2, lambda2, lambda2),
  draw_dist = TRUE,
  showN = TRUE
)
```